On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-09-17 documents/distribution.tex
Personal device

\begin{center}
	{\bf \cite{Microwave2009} already mention this effect; \cite{Elastic} does a much better analysis than we do.}
\end{center}

@@

>>>>

\begin{center}
	{\bf \cite{Microwave2009} already mention this inhomogeneity; \cite{Elastic} perform a much better analysis than we do.}
\end{center}

@@

Inputting this yield stress distribution produces an inactivation field distribution that is far higher than that of \cite{Efficient2015}'s experimental data by some 200 V/m.

Let us therefore re-examine the reason why.

### 2020-09-17 documents/paper.tex
Personal device

We therere demonstrate this form factor because, superficially, there are fewer people than there are places.

On the other hand, a personal device may present issues with participation and production volume.

@@

{\color{red} speculation \{ }

@@

Surprisingly, there is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019]. Such scholarly silence is usually an indicator that a technique is impossible for reasons so obvious they scarcely bear repeating.

>>>>

@@

@@

there is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019]. Such scholarly silence is usually an indicator that a technique is impossible for reasons so obvious they scarcely bear repeating.
